Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
Extended scenario

>>>>

To give more context to the scenario, vulnerable.com can be a cloud storage service. 
The attacker infiltrates the target by uploading a polyglot to the service and embed it 
on attacker.com. While authenticated to vulnerable.com, the unsuspecting victim visits attacker.com, the embedded 
polyglot is activated and extracts all the files stored in the victims account.
